Red, Blue, or Grey? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
paper final draft
made one corrections on label

```{r}
#| echo: false
#| label: fig-recency_effect
#| warning: false
#| message: false
#| layout-ncol: 2
#| layout-nrow: 1
#| fig-height: 3
#| fig-width: 4

@@

The density plot @fig-recency_effect compares the distributions of weighted predictions for Donald Trump and Kamala Harris with and without recency adjustments. For both candidates, predictions are generally concentrated in similar ranges, with Donald Trump’s support mostly clustering around 40-60% and Kamala Harris’s around 30-50%. This similarity in distribution suggests that the recency adjustment does not cause a big shift in overall predictions for either candidate. However, some differences are noticeable in the tails of the distributions, particularly for Donald Trump, where predictions with recency adjustments exhibit a slightly tighter distribution, potentially indicating a more stable support level as the election date nears.

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-recency_effect
#| fig-cap: "Weighted Prediction with and without Recency Effect"
#| fig-subcap: ["Donald Trump", "Kamala Harris"]
#| layout-ncol: 2
#| layout-nrow: 1
#| fig-height: 3
#| fig-width: 4

@@

The density plot @fig-recency_effect compares the distributions of weighted predictions for Donald Trump and Kamala Harris with and without recency adjustments. For both candidates, predictions are generally concentrated in similar ranges, with Donald Trump’s support @fig-recency_effect-1 mostly clustering around 40-60% and Kamala Harris’s  @fig-recency_effect-2 around 30-50%. This similarity in distribution suggests that the recency adjustment does not cause a big shift in overall predictions for either candidate. However, some differences are noticeable in the tails of the distributions, particularly for Donald Trump, where predictions with recency adjustments exhibit a slightly tighter distribution, potentially indicating a more stable support level as the election date nears.
